The story begins in ancient Greek times,
with discrete approximations to obtain continuous areas by the method of exhaustion.
In particular, Archimedes (287-212 BC) evaluated sums of squares while finding
the spiral's area~\cite{pengelley2002bridge},
analogous to what we have nowadays
\begin{align*}
  1^2 + 2^2 + 3^2 + \cdots n^2 = \frac{n(n+1)(2n+1)}{6}.
\end{align*}

Moving to early modern Europe (1636),
Pierre de Fermat (1601-1665) referred to the problem
of finding formulas for sums of powers
\textit{... perhaps the most beautiful problem of all arithmetics},
in his correspondence with Blaise Pascal (1623-1662).
Fermat's contribution to the topic was quite remarkable indeed,
as he revived the study of figurate numbers and investigated
their arithmetic properties,
including what is now known as Fermat's polygonal number theorem.
Application of polygonal numbers in sums of powers
is extensively discussed in~\cite[(2020)]{Marko2020}.

Meanwhile, Johann Faulhaber (1580-1635) worked on the problem of sums of powers,
writing his famous book \textit{Academia Algebrae}~\cite[(1631)]{faulhaberacademia}.
Faulhaber's contribution was great indeed, because Johann managed
to compute formulas up to
$\KnuthRFoldSum{1}{n}{25} = 1^{25}+2^{25}+ \cdots + n^{25}$,
which is quite impressive.
Imagine to derive the formula back in 17-th century, without computers.
Faulhaber explicitly tabulated formulas through the seventeenth
power and provided sufficient information for determining higher cases,
including the twenty-fifth power.
Knuth later reconstructed the latter computation.
Faulhaber actually discovered deep structural patterns,
particularly for odd powers expressed as polynomials
in triangular numbers.
What he lacked was a completely general symbolic formula.

The major breakthrough was achieved by Jacob Bernoulli (1665-1705) in his work
entitled
\textit{Ars coniectandi}~\cite[(1713)]{bernoulli1713ars}, published postmortem.
In the work, Jacob introduced Bernoulli numbers (named after him later),
thus allowing for arbitrary powers to be summed up
\begin{align*}
  \sum_{k=1}^{n} k^p = \frac{1}{p+1} \sum_{r=0}^{p} \binom{p+1}{r} B_r n^{p+1-r}
\end{align*}
It assumes that $B_1 = +\frac{1}{2}$.
The choice of convention for $B_1$ has a long historical background;
see~\cite{luschny2021manifesto,luschny2020introduction}
for a detailed discussion.
Therefore, Bernoulli managed to contribute the missing capstone to
Faulhaber's work, making it symbolically complete.
In fact, the formula above is commonly referred to as Faulhaber's formula,
although the modern Bernoulli-number formulation originates with Bernoulli's
great work.

During the eighteenth and nineteenth centuries,
the theory was further developed by Euler, Stirling, Jacobi,
and others through connections with finite differences, interpolation,
and special number sequences.

Fast-forward to 1993, Donald Knuth revisited the topic of sums of powers,
giving it a new direction of development.
Based on works of Carl Gustav Jacobi (1804-1851),
and Gessel-Viennot~\cite[(1989)]{gessel1989determinants}, Knuth reviewed Faulhaber's
work from a completely different angle, by using modern
enumerative combinatorics techniques.
Remarkably, Knuth's contribution does not necessarily involve Bernoulli numbers,
instead he derived formulas for power sums
by utilizing special numbers (e.g Stirling, central factorial),
and Binomial coefficients.
In addition, Knuth introduced
a remarkably convenient notation for $r$-fold sums of powers $\KnuthRFoldSum{r}{n}{m}$,
which we use in this work.

In this manuscript, we reveal the role of Newton's interpolation formula
in the process of deriving closed formulas for sums of powers.
As the main result, this paper proposes an algorithm to derive closed formulas
for sums of powers, by utilizing variations of Newton's interpolation formula,
combined with hockey-stick family binomial identities.
As results show, there are infinitely
many variations of closed formulas for sums of powers.
